\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-23 pldi/microbenchmarks-table.tex
Half-way pass over eval

\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} lllllll}
\toprule
Script ~&~ Structure & Input &Seq Time & Script Size(\todo{20, 100}) &Compile Time (\todo{20, 100}) & Highlights \\
\midrule
\tti{grep} ~&~ $3\times$\tsta & 1~GB & 80m9.607s & \todo{\#Commands} & 0.063s\qquad 0.966s & complex NFA regex \\
\tti{sort} ~&~ $\tsta, \tpur$ & 10~GB & 23m49.044s & \todo{\#Commands} & 0.201s\qquad 2.006s & \tti{sort}ing \\
\tti{top-n} ~&~ $2\times\tsta, 4\times\tpur$ & 10~GB & 72m53.786s & \todo{\#Commands} & 0.170s\qquad 3.341s & double \tti{sort}, \tti{uniq} reduction \\
\tti{wf} ~&~ $3\times\tsta, 3\times\tpur$ & 10~GB & 22m31.907s & \todo{\#Commands} & 0.165s\qquad 3.325s & double \tti{sort}, \tti{uniq} reduction \\
\tti{grep-light} ~&~ $3\times$\tsta & 100~GB & 1m38.212s & \todo{\#Commands} & 0.035s\qquad 0.356s & $3\times$\tsta \\
\tti{spell} ~&~ $4\times\tsta, 3\times\tpur$ & 1~GB & 8m1.131s & \todo{\#Commands} & 0.311s\qquad 6.655s & comparisons (\tti{comm}) \\
\tti{shortest-scripts} ~&~ $5\times\tsta, 2\times\tpur$ & \todo{UNKNOWN} & 28m26.746s & \todo{\#Commands} & 0.305s\qquad 6.729s & \todo{extensive file-system operation} \\
\tti{diff} ~&~ \todo{TODO} & 10~GB & 26m50.085s & \todo{\#Commands} & 0.312s\qquad 4.569s & non-parallelizable \tti{diff}ing \\
\tti{optimized bi-grams} ~&~ $3\times$\tsta, \tpur & 10~GB & 123m54.946s & \todo{\#Commands} & 0.136s\qquad 2.674s & optimized version of bigrams \\
\bottomrule
\end{tabular*}

>>>>

\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} lllllllll}
\toprule
Script ~&~ Structure & Input &Seq. Time & \multicolumn{2}{l}{\#Nodes(16, 64)} &\multicolumn{2}{l}{Compile Time (16, 64)} & Highlights \\
\midrule
grep ~&~ $3\times\tsta$ & 1~GB & 79m35.197s & 49 & 193 & 0.056s & 0.523s & complex NFA regex \\
sort ~&~ $\tsta, \tpur$ & 10~GB & 21m46.807s & 77 & 317 & 0.090s & 1.083s & \tti{sort}ing \\
top-n ~&~ $2\times\tsta, 4\times\tpur$ & 10~GB & 78m45.872s & 96 & 384 & 0.145s & 1.790s & double \tti{sort}, \tti{uniq} reduction \\
wf ~&~ $3\times\tsta, 3\times\tpur$ & 10~GB & 22m30.048s & 96 & 384 & 0.147s & 1.809s & double \tti{sort}, \tti{uniq} reduction \\
grep-light ~&~ $3\times\tsta$ & 100~GB & 1m38.212s & 49 & 193 & 0.031s & 0.163s & IO-intensive, computation-light \\
spell ~&~ $4\times\tsta, 3\times\tpur$ & 3~GB & 25m7.560s & 69 & 261 & 0.104s & 1.038s & comparisons (\tti{comm}) \\
shortest-scripts ~&~ $5\times\tsta, 2\times\tpur$ & 85~MB & 28m45.900s & 142 & 574 & 0.328s & 4.657s & long \tsta pipeline ending with \tpur \\
diff ~&~ $2\times\tsta, 3\times\tpur$ & 10~GB & 25m49.097s & 125 & 509 & 0.186s & 2.341s & non-parallelizable \tti{diff}ing \\
bi-grams ~&~ $3\times\tsta, 3\times\tpur$ & 3~GB & 38m9.922s & 109 & 445 & 0.146s & 1.716s & stream shifting and merging \\
bi-grams-opt ~&~ $3\times\tsta, \tpur$ & 3~GB & 38m21.501s & 63 & 255 & 0.117s & 1.482s & optimized version of bigrams \\
set-diff ~&~ $5\times\tsta, 2\times\tpur$ & 10~GB & 51m32.313s & 155 & 635 & 0.321s & 4.358s & two pipelines merging to a \tti{comm} \\
sort-sort ~&~ $\tsta, 2\times\tpur$ & 10~GB & 31m26.147s & 78 & 318 & 0.092s & 1.077s & parallelizable \tpur after \tpur \\
\bottomrule
\end{tabular*}
